### 2021-04-26 Paper/Main.tex
Updates from Overleaf

\begin{center}
\input{Paper/prelim_beta}\\
\textbf{Table 5:} beta decile by estimated coefficients for the  five fama french factors and EMP factor
\end{center}
% beta p vals
\begin{center}
\input{Paper/p_vals_beta_prelim}\\
\textbf{Table 6:} Size decile by p-values for table 5
\end{center}
% pass 2
\begin{center}
\input{Paper/pass_2}\\
\textbf{Table 7:} second pass results for the size and beta decile portfolios
\end{center}

@@

\bibliography{Matt_Bib.bib}{}
\bibliographystyle{plain}

\newgeometry{margin=.15in}
\input{Code/data/size_summary_stat_size}\\

\section{Appendix}
\vspace{1cm}
\textbf{Table 2:} This table shows the mean results by decile before any regressions\\
\vspace{1cm}

>>>>

\begin{center}
\input{Code/data/size_output_inital}
\\
\textbf{Table 5:} beta decile by estimated coefficients for the  five fama french factors and EMP factor
\end{center}
% beta p vals
\begin{center}
\input{Paper/p_vals_beta_prelim}\\
\textbf{Table 6:} Size decile by p-values for table 5
\end{center}
% pass 2
\begin{center}
\input{Paper/pass_2}\\
\textbf{Table 7:} second pass results for the size and beta decile portfolios
\end{center}

@@

\bibliography{Matt_Bib.bib}{}
\bibliographystyle{plain}
\singlespacing
\newgeometry{margin=.15in}

\section{Appendix}
\input{Code/data/size_summary_stat_size}\\
\textbf{Table 2:} This table shows the mean results by decile before any regressions\\
\vspace{1cm}

\begin{center}
\input{Code/data/beta_output_inital}\\
\textbf{Table 3:} Beta decile by estimated coefficients for the  five fama french factors and EMP factor\\
\end{center}
\vspace{1cm}
\begin{center}
\input{Code/data/size_output_inital}\\
\textbf{Table 4:} Size decile by estimated coefficients for the  five fama french factors and EMP factor\\
\end{center}

\begin{center}
    \input{Code/data/FF_pass_2}\\
    \textbf{Table 4:} second pass results for the size and beta decile portfolios\\
\end{center}

\begin{center}
    \input{Code/data/FF_pass_2_no_ESG}\\
    \textbf{Table 5:} second pass results for the size and beta decile portfolios without ESG factor\\
\end{center}
